Indexing Variation Graphs\footnote{This work was supported by the Wellcome Trust grant 098051.}

### 2016-08-10 paper/paper.tex
Fixed some numbers

\begin{table}[t!]
\begin{center}
\caption{Index sizes with different orders $k$ of the path graph. Number of \kmer{k}s and nodes in the pruned de~Bruijn graph in billions; index size in gigabytes and in bits per \kmer{k} for the graph ($\BWT$, $\bvIN$, and $\bvOUT$), the index (graph, $B_{S}$, $B_{V}$, and $V_{S}$), and the index with the extensions from Section \ref{sect:extensions}.}\label{table:indexes}
\begin{tabular}{c|cc|c|c|c}
\hline
\textbf{Order} & \textbf{\kmer{k}s} & \textbf{Nodes} & \textbf{Graph} & \textbf{Index} & \textbf{With extensions} \\
\hline
 32 & 6.20G & 4.37G & 3.28 GB / 4.55 bits & 9.97 GB / 13.8 bits & 13.6 GB / 18.9 bits \\
 64 & 16.7G & 5.24G & 3.93 GB / 2.03 bits & 9.19 GB / 4.74 bits & 14.1 GB / 7.27 bits \\
128 &  116G & 5.76G & 4.29 GB / 0.32 bits & 9.17 GB / 0.68 bits & 15.2 GB / 1.12 bits \\
\hline
\end{tabular}
\end{center}
\end{table}

>>>>

\begin{table}[t!]
\begin{center}
\caption{Index sizes with different orders $k$ of the path graph. Number of \kmer{k}s and nodes in the pruned de~Bruijn graph in billions; index size in gigabytes and in bits per \kmer{k} for the graph ($\BWT$, $\bvIN$, and $\bvOUT$), the index (graph, $B_{S}$, $B_{V}$, and $V_{S}$), and the index with the extensions from Section \ref{sect:extensions}.}\label{table:indexes}
\begin{tabular}{c|cc|c|c|c}
\hline
\textbf{Order} & \textbf{\kmer{k}s} & \textbf{Nodes} & \textbf{Graph} & \textbf{Index} & \textbf{With extensions} \\
\hline
 32 & 6.20G & 4.37G & 3.28 GB / 4.55 bits & 9.97 GB / 13.8 bits & 13.6 GB / 18.9 bits \\
 64 & 16.7G & 5.24G & 3.93 GB / 2.03 bits & 9.19 GB / 4.74 bits & 14.1 GB / 7.27 bits \\
128 &  116G & 5.73G & 4.29 GB / 0.32 bits & 9.17 GB / 0.68 bits & 15.2 GB / 1.12 bits \\
\hline
\end{tabular}
\end{center}
\end{table}
